\section{Dance Recital}
\label{dancerecital}
\href{https://open.kattis.com/problems/dancerecital}{View on Kattis}\\
\textbf{Tags:} Brute Force, Permutations\\
\subsection{Problem Description}

We are given a list of dance routines, each of which describe a cast of dancers
that will be needed to perform each routine. We want to minimize the number of
times a dancer will perform in back to back routines (called a "quick change").
For example, in the ordering:
\begin{verbatim}
ABC
ABEF
DEF
ABCDE
FGH
\end{verbatim}
There are 6 quick changes (A and B between the 1st and 2nd dances, E and F
between the 2nd and 3rd, and D and E between the 3rd and 4th dances). \\
\hfill\break
However, if we use the ordering:
\begin{verbatim}
ABEF
DEF
ABC
FGH
ABCDE
\end{verbatim}
There are only 2 quick changes (E and F between the 1st and 2nd dances). Given
a list of \textbf{N} routines ($2 \leq N \leq 10$), consisting of dancers
described using only uppercase A-Z letters, determine the minimum number of
quick changes.
\subsection{Algorithm}

Since $10! = 3628800$ is rather tractable, we can brute-force this. However,
in order to make the computation performed at each step as fast as possible,
we will pre-compute the number of quick changes between every pair of dances
and store this ahead of time. Then, each step of the brute force calculation
just requrires us to iterate over the permuted values in order.\\
\hfill\break
Because brute-forcing all permutations of the given values is not the key
part of this excercise, we will rely on our brute-force library to do the
heavy lifting. \\
\hfill\break
\textbf{Time Complexity:} $\mathcal{O}(N! + N \cdot P^2)$\\
\textbf{Space Complexity:} $\mathcal{O}(N(N+P))$\\
Where \textbf{N} is the number of routines ($2 \leq N \leq 10$), and \textbf{P}
 is the number of different dancers ($1 \leq P \leq 26$).
\subsection{Implementation}
\lstinputlisting[language=Java]{Solutions/DanceRecital.java}
\pagebreak
