\section{Hidden Password}
\label{hiddenpassword}
\href{https://open.kattis.com/problems/hidden}{View on Kattis}\\
\textbf{Tags:} Strings\\
\subsection{Problem Description}
We are given a password and a message that is supposed to secretly contain the
given password. We must determine if the password is successfully hidden in the
message. In order for this to be the case, the following must hold true:
\begin{itemize}
  \item Denote the password as $P = \{c_{1}, c_{2}, ..., c_{p}\}$.
  \item $c_{1}$ should be the first character in the password to appear in the
  message.
  \item Let $S^{c_{i}}$ denote all characters in the message following the
  character that corresponds to $c_{i}$.
  \item Then the first character in $S^{c_{i}}$ that appears in $P[(i+1) ... p]$
  must equal $c_{i+1}$, for all $ 1 \leq i \leq p-1$.
\end{itemize}
\subsection{Algorithm}
Our algorithm will be a straight-forward implementation of the given check. We
will keep a pointer, \textit{passwordIndex} to which character in the password
we must find next, and iterate over all characters in the message. For each
character \textit{c}, if $c = P[passwordIndex]$, then we increment
\textit{passwordIndex}. Once \textit{passwordIndex} equals $|P|$, we know we
have a match. However, if $c \neq P[passwordIndex]$ and
$\exists \quad i \quad (passwordIndex < i \leq |P|) \quad s.t. \quad c = P[i]$,
then the message and password do not match. Furthermore, if we reach the end of the
message, and $passwordIndex < |P|$, then the message and password do not match.\\
\hfill\break
\textbf{Time Complexity:} $\mathcal{O}(|P| \cdot |S|)$\\
\textbf{Space Complexity:} $\mathcal{O}(|P| + |S|)$\\
Where $|P|$ ($3 \leq |P| \leq 8$) is the length of the password and
$|S|$ ($10 \leq |S| \leq 40$) is the length of the message.
\pagebreak
\subsection{Implementation}
\lstinputlisting[language=Java]{Solutions/HiddenPassword.java}
\pagebreak
