\section{Kitchen Measurements}
\label{kitchenmeasurements}
\href{https://open.kattis.com/problems/kitchen}{View on Kattis}\\
\textbf{Tags:} Search, UCS\\
\subsection{Problem Description}

We are given a set of \textit{N} cups $(2 \leq N \leq 5)$ of decreasing
capacities $c_{1}, c_{2}, ..., c_{N}$. The first (and largest) cup is initially
full of water, and all other cups are empty. We are also given a target volume
\textit{V}. Our goal is to end up with exactly \textit{V} units of water in the
first cup, only by pouring water from one cup to another until either the source
cup is empty or the destination cup is full.\\
\hfill\break
If this is impossible, need to say so. Otherwise, we should determine the
minimum amount of liquid that must be poured to achieve the goal.
\subsection{Algorithm}

The solution to this can be derived by performing a Uniform Cost Search, or
Dijkstra's Algorithm. The focus of this exercise will be on determining what
the state space will be, the successor function, and how we will determine
whether or not we are at a goal state. Because performing the search is not the
focus of this, we will be using the search library to perform the acutal search.\\

\textbf{State Space}\\
We will define a state as $\{w_{1}, w_{2}, ... w_{N}\}$, the amount of water in each
cup in the given state. Two states $s_{1} = \{u_{1}, ... u_{N}\}$ and
$s_{2} = \{v_{1}, ... v_{N}\}$ are identical if and only if
$\forall\, i,\, 1 \leq i \leq N,\, v_{i} = u_{i}$.\\

\textbf{Goal State}\\
A given state $s = \{w_{1}, w_{2}, ... w_{N}\}$ is a goal state if and only if
$w_{1} = V$.\\

\textbf{Neighbor Function}\\
We can use the following algorithm to find all neighbors:
\begin{algorithmic}
  \State Let $distance$ be a map of neighbors to distance.
  \For{$src \gets 1$ to $N$}
    \For{$dst \gets 1$ to $N$}
      \If {$src \neq dst$}
        \State $pour \gets \min(w_{src}, c_{dst} - w_{dst})$
        \If {$pour > 0$}
          \State $\{w'_{1}, ... w'_{N}\} \gets \{w_{1}, ... w_{N}\}$
          \State $w'_{src} \gets w'_{src} - pour$
          \State $w'_{dst} \gets w'_{dst} + pour$
          \State $distance (\{w'_{1}, ... w'_{N}\}) \gets pour$
        \EndIf
      \EndIf
    \EndFor
  \EndFor
\end{algorithmic}
With all of the following defined, we can rely on the UCS class in the search
library to find the optimal procedure, if it exists.\\
\hfill\break
\textbf{Time Complexity:} $\mathcal{O}(N^2 \cdot |S| \cdot \log(|S|))$\\
\textbf{Space Complexity:} $\mathcal{O}(|S|)$\\
Where $N$ is the number of cups, and $|S|$ is the number of different states
we can explore. This is loosely bound by ${\displaystyle \prod_{i=1}^{N} c_{i}}$,
but is significantly less than this value in practice.
\subsection{Implementation}
\lstinputlisting[
  language=Java,
  lastline=35
]{Solutions/KitchenMeasurements.java}
\pagebreak
\lstinputlisting[
  language=Java,
  firstline=37
]{Solutions/KitchenMeasurements.java}
\pagebreak
