\section{Pyro Tubes}
\label{pyrotubes}
\href{https://open.kattis.com/problems/pyro}{View on Kattis}\\
\textbf{Tags:} Bit Manipulation, Implementation\\
\subsection{Problem Description}
We are given a list of values of brightness to be achieved by illuminating a
selection of tubes. The first tube has a brightness of 1, and each subsequent
tube has double the brightness of the previous tube. For each value, we need to
calculate the number of alternative brightness values. For an alternative value
to be valid, it must satisfy the following:
\begin{itemize}
  \item The alternate value must be greater than the original.
  \item The alternate must be another value in the given list.
  \item The alternate must be achieved by changing no more than 2 tubes from the
  original
\end{itemize}
\subsection{Algorithm}
The key to this is to realize that the tubes simply correspond to bits in the
binary representation of each value. To solve this, we can iterate over all
combinations of 1 or 2 bits in the given range ($2^{0}$ to $2^{17}$, per the
problem statement). We can simply xor the original value with these bits to change
them. If the result is greater than the original, and is in a set containing
all values in the list, we can increment the counter for this value.\\
\hfill\break
\textbf{Time Complexity:} $\mathcal{O}(N \cdot \log^{2}L)$\\
\textbf{Space Complexity:} $\mathcal{O}(N)$\\
Where $N$ is the number of tubes, and $L$ is the largest possible brightness value.
\pagebreak
\subsection{Implementation}
\lstinputlisting[language=Java]{Solutions/PyroTubes.java}
\pagebreak
