\section{The Agglomerator}
\label{theagglomerator}
\href{https://open.kattis.com/problems/agglomerator}{View on Kattis}\\
\textbf{Tags:} Algebra, Geometry\\
\subsection{Problem Description}
We are given the initial positions, initial velocities, and sizes of a
collection of circular droplets in a 2-D grid. When two droplets touch one
another, they will merge into a single droplet. This new droplet's location and
velocity will be the area-weighted average of the 2 initial droplet's locations
and velocities. We need to simulate the movement of the droplets until no more
merges will occur. Luckily, the droplets have the following constraints:

\begin{itemize}
  \item The original droplets do not touch each other.
  \item When a new droplet is formed from a merge, the new droplet will be a
  distance of at least $0.001$ from all other droplets.
  \item Changing the radius of any drop by $\pm 0.001$ will not affect whether
  it collides with any other drop.
  \item All collisions will be at least $0.001$ seconds apart.
  \item No droplets will merge after $t = 10^{9}$ seconds.
\end{itemize}

Given these constraints, determine how many droplets will be left at the end,
and the time of the last merge.\\

\subsection{Algorithm}

To find when (and if) two drops $a$ and $b$ will collide, we can use some basic
algebra. We need to solve for the first time $t$ where the drop's distance is
equal to the sum of their radii:

\begin{equation}
\Bigg | \bigg ( \begin{pmatrix}x_{a} \\ y_{a}\end{pmatrix} + t \cdot
  \begin{pmatrix}v_{ax} \\ v_{ay}\end{pmatrix} \bigg ) - \bigg (
  \begin{pmatrix}x_{a} \\ y_{a}\end{pmatrix} + t \cdot
  \begin{pmatrix}v_{ax} \\ v_{ay}\end{pmatrix} \bigg ) \Bigg |
  =  r_{a} + r_{b}
\end{equation}

To simplify calculatations, let us say
$\begin{pmatrix}x_{a} \\ y_{a}\end{pmatrix} +
\begin{pmatrix}x_{b} \\ y_{b}\end{pmatrix} =
\begin{pmatrix}d_{x} \\ d_{y} \end{pmatrix}$,
$\begin{pmatrix}v_{ax} \\ v_{ay}\end{pmatrix} +
\begin{pmatrix}v_{bx} \\ v_{by}\end{pmatrix} =
\begin{pmatrix}d_{vx} \\ d_{vy}\end{pmatrix}$, and
$r_{a} + r_{b} = s_{r}$.\\

Then, we can reduce the given equality to a quadratic equation:

\begin{equation}
  \big ( d_{vx}^{2} + d_{vy}^{2} \big ) \cdot t^{2} +
  \big ( 2 d_{x} d_{vx} + 2 d_{y} d_{vy} \big ) \cdot t +
  \big ( d_{x}^{2} + d_{y}^{2} - s_{r}^{2} \big ) = 0
\end{equation}

and solve using the quadratic formula
${\big ( -b \pm \sqrt{b^{2} - 4ac} \big ) } / {2a}$, where
$a$ is the coefficient of $t^2$, $b$ is the coefficient of $t$, and $c$ is the
constant term.\\

Because of the constraint that there will be no droplets intersecting at the
start or immediately following a merge, we know that if we look for collisions
at those times, the two solutions for this equation will always have the same
sign. Thus, we can always use the lower solution, which (because $a$ must be
positive) is guaranteed to be the solution in which the root of the determinant
is subtracted. If the determinant or the solution is negative, then the pair
of droplets will not intersect in the future. Otherwise, they will intersect
after the given amount of time.\\

Now that we have a means for finding the time of intersection, we can simulate
the droplets. This can be done as follows:
\hfill\break
\begin{algorithmic}
  \State Let $D$ be a set containing all droplets.
  \State $time \gets 0$
  \While{Another intersection will occur}
    \State Let $a$, $b$ be the droplets that will intersect next, after time $t$.
    \For{$d$ in $D$}
      \State $d \gets advance(d, t)$
    \EndFor
    \State $time \gets time + t$
    \State $D \gets D - a$
    \State $D \gets D - b$
    \State $D \gets D + merge(a, b)$
  \EndWhile
  \State Return $|D|$, $time$
\end{algorithmic}
\hfill\break
Advancing and merging drops simply involves updating the positions of the
droplets as specified in the problem statement.\\
\hfill\break
\textbf{Time Complexity:} $\mathcal{O}(N^{3})$\\
\textbf{Space Complexity:} $\mathcal{O}(N)$\\
Where $N$ is the number of droplets $(2 \leq N \leq 100)$.
\pagebreak
\subsection{Implementation}
\lstinputlisting[
  lastline=45,
  language=Java
  ]{Solutions/Agglomerator.java}
\pagebreak
\lstinputlisting[
  firstline=47,
  lastline=95,
  language=Java
  ]{Solutions/Agglomerator.java}
\pagebreak
\lstinputlisting[
  firstline=97,
  language=Java
  ]{Solutions/Agglomerator.java}
\pagebreak
